---
title: "Math 443: Linear Algebra II"
---

## Welcome

Welcome to Math 443, a second course in linear algebra.  We'll be studying *Matrix Mathematics: A Second Course in Linear Algebra* by Garcia and Horn. (Here's a [Google Books preview](https://www.google.com/books/edition/Matrix_Mathematics/gv9xzwEACAAJ?hl=en).)

Through the semester, we'll be working together to create a collection of high quality solutions for many of the problems in this text. We'll be using `quarto` files with `R` and `RStudio` to create high quality solutions. We'll use `git` to share our work on `GitHub`. We'll utilize `python` for computations. 


### Table of Submissions

```{r include=FALSE}
library(tidyverse)
library(DT)

# Code copied from ChatGPT
# List of URLs for your CSV files
url_list <- c(
  "https://byuim443.github.io/Kip-Smith/file_list.csv",
  "https://byuim443.github.io/DayP/file_list.csv",
  "https://byuim443.github.io/PlanetDragons/file_list.csv",
  "https://byuim443.github.io/G/file_list.csv",
  "https://byuim443.github.io/Ajax/file_list.csv",
  "https://byuim443.github.io/Ewing/file_list.csv",
  "https://byuim443.github.io/Cub3rkid/file_list.csv",
  "https://byuim443.github.io/mathmanican/file_list.csv"
)

# Function to read CSV with error handling
#read_csv_safe <- possibly(read_csv, otherwise = NULL)

# Function to read CSV with error handling and check for zero rows
read_csv_safe <- function(url) {
  data <- tryCatch(
    read_csv(url),
    error = function(e) NULL
  )
  
  if (!is.null(data) && nrow(data) > 0) {
    return(data)
  } else {
    return(NULL)
  }
}

# Map the URLs to read_csv_safe
data_list <- map(url_list, read_csv_safe)

# Filter out NULL elements (occurred when 404 error)
data_list <- compact(data_list)

# Combine the data frames if needed
combined_data <- 
  bind_rows(data_list) %>% 
  arrange(-Chapter,-Problem)

```

Here's all the contributed submissions in a searchable table.

```{r echo=FALSE}
DT::datatable(combined_data, 
              escape = FALSE, 
              rownames=FALSE,
              options = list(pageLength = 10))
```

### [Setup](setup.qmd)

We'll be using multiple software packages this semester.  The setup section will help you get things started. 

### Syllabus

The syllabus is located in [Canvas](https://byui.instructure.com/courses/271212), along with discussion boards for uploading your prep work. 

### [FAQ](faq.qmd)

Look here for common questions on the course.
